Outline flowCore paper

### 2008-04-15 paper/outline.tex
comments and notes
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@31090 bc3139a8-67e5-0310-9ffc-ced21a209358

@@

@@

@@

>>>>

{\bf NLM:} Only a couple of commercial software (e.g., FlowJo and
DeNovo) allows the user to analyse batch of FCS files.  Only a few
allows export in XML (e.g., FlowJo). Most commercial software require
a Microsoft Windows platform whereas flowCore runs on multiple
operating systems including Windows, Mac OS X and Unix.

@@

{\bf NLM:} How about mentioning PlateCore here?

@@

{\bf NLM:} example: cite flowClust and floViz paper?

@@

{\bf NLM:} We could illustrate/summarize:
\begin{itemize}
\item the power of subsetting: for example to manipulate 
patient below a certain age or of the same sex...
\item Gating: filterSet strategy, kmeanFilter
\item visualization adding metadata as parameter
example: cite flowViz paper
\end{itemize}
